Variation in distance between consecutive animal locations

### 2021-07-06 distributions_paper/rudolph_distributions.Rmd
Damn, it has been so long I don't even remember what this is. Cross fingers nothing breaks.

@@

>>>>

**2021-05-03**

- Explain what levy processes are and why they are suggested. Random search for resources. 
- Classical random walks for homogeneous environments, and in more complex environments, use mixtures of these 'classical' random walks, to show the animals adaptability to the changes in the environment. 
- Levy walks claimed to be more efficient than classical random walks for search or activity patterns.
- Levy walks are non-oriented and superdiffusive. Interesting too because they may be involved when the random variable follows a power-law distribution. 
- Classical random walks have step lengths distributed with finite variance, and in their simplest form, both their step length and turning angles are uniformly distributed. Levy walks are also uncorrelated and unbiased, like mere random walks, but their step lengths are characterized by infinite variance (i.e. drawn from a heavy-tail distribution). simplest example with a pareto distribution. [Benhamou 2007]

Bartumeus 2007
Levy-type processes can be relevant in large-scale animal movement.

@@

# jmp <- aracari_df %>% 
#   drop_na(dist) %>% 
#   filter(id == 5) %>% 
#   dplyr::select(dist, dt) %>% 
#   mutate(vel = dist/(dt/60))
# 
# save(jmp, file = "ex_data.RData")
